LAGOS lake depth

### 2021-08-10 figures/02_depth_model.Rmd
compute and arrange complex table 1 showing shape/res sensitivity, #27

```{r depth_model_metrics, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=2.6, fig.width=4}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ " ",
    TRUE ~ paste0(rmse, " m"))) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

>>>>

```{r depth_model_metrics, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=2.6, fig.width=4}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds")[[1]] %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ " ",
    TRUE ~ paste0(rmse, " m"))) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

### 2021-08-10 tables/02_model_metrics.Rmd
linting?
linting
compute and arrange complex table 1 showing shape/res sensitivity, #27

dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = round(as.numeric(rmse), 1)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_character_,
    TRUE ~ paste0(rmse, " m"))) %>%
  mutate(mape = as.numeric(mape)) %>%
  mutate(mape = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_character_,
    TRUE ~ paste0(round(mape, 0), " %"))) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

options(knitr.kable.NA = '-')
knitr::kable(dt_metrics, digits = 2, format = "markdown")

@@

@@

options(knitr.kable.NA = '-')
knitr::kable(dt_metrics, digits = 2, format = "markdown")

>>>>

tidy_grid_metrics <- function(x) {
  res <- x %>%
    mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
    mutate(rsq = as.numeric(rsq)) %>%
    mutate(rsq = case_when(
      as.character(model) == "maxdepth_true_true" ~ NA_real_,
      TRUE ~ rsq)) %>%
    mutate(rmse = round(as.numeric(rmse), 1)) %>%
    mutate(rmse = case_when(
      as.character(model) == "maxdepth_true_true" ~ NA_character_,
      TRUE ~ paste0(rmse, " m"))) %>%
    mutate(mape = as.numeric(mape)) %>%
    mutate(mape = case_when(
      as.character(model) == "maxdepth_true_true" ~ NA_character_,
      TRUE ~ paste0(round(mape, 0), " %"))) %>%
    mutate(model = gsub("maxdepth_", "", model)) %>%
    mutate(model = gsub("false", "proxy", model)) %>%
    tidyr::separate(model, c("slope", "distance")) %>%
    dplyr::select(slope, distance, everything(), -.estimator)
  res
}

dt_metrics <- tidy_grid_metrics(
  readRDS("../data/01_depth_model/depth_grid_metrics.rds")[[1]])

options(knitr.kable.NA = "-")
knitr::kable(dt_metrics, digits = 2, format = "markdown")

@@

```{r 02_model_sensitivity, eval=TRUE}
dt_metrics_sensitivity <- lapply(
  readRDS("../data/01_depth_model/depth_grid_metrics.rds"), function(x)
    tidy_grid_metrics(x))

labels <- c("All", "Res only", "NL only", "convex only", "concave only")
dt_metrics_sensitivity <- lapply(
  seq_len(length(dt_metrics_sensitivity)), function(i) {
    res <- dplyr::mutate(dt_metrics_sensitivity[[i]], label = labels[i]) %>%
      dplyr::relocate(label)
    res$label[2:4] <- NA
    res
  })

options(knitr.kable.NA = "-")
knitr::kable(do.call("rbind", dt_metrics_sensitivity),
  digits = 2, format = "markdown")
```

@@

options(knitr.kable.NA = "-")
knitr::kable(dt_metrics, digits = 2, format = "markdown")
